Temporal stability in human interaction networks: sector sizes, topological prominence and time activity

### 2015-10-07 paper.tex
revisada evolucao e audiovisualizacao dos dados

The covariance matrix 
$\mathbf{C}$ is the correlation matrix because $\mathbf{X'}$ is normalized.
Therefore, $\mathbf{C}$ is also directly observed as a first clue for patterns
by the most simple associations:
low absolute values indicate low correlation (and a possible independence);
high values indicate positive correlation;
negative values with a high absolute value indicate negative correlation.
\subsection{Evolution and visualization of the networks}\label{sec:viz}
The evolution of the networks was observed within sequences of snapshots. with a fixed number of messages,
Each of these sequences had a fixed number of messages, the window size $ws$,
which was considered with different shifts in the message timeline to obtain snapshots.
In each snapshot was performed both the PCA with topological metrics and the Erd\"os sectioning.  
The values of $ws$ employed were 50, 100, 200, 400, 500, 800, 1000, 2000, 2500, 5000 and 10000.
Variations in the number of vertices, edges
and other network characteristics
are exposed in Section~\ref{si:frac}
of the Supporting Information document.

Networks were visualized with animations, sonifications,
image galleries and online gadgets developed specifically for this research~\cite{animacoes,galGMANE,appGMANE}.
Such \emph{audiovisualizations} were crucial to guide the research into the most important features of network evolution.
Furthermore, the size of the three Erd\"os sectors could be visualized in a timeline fashion.
Visualization of network structure was especially useful in the initial inspection of data and of the structures derived from the email lists.

>>>>

The covariance matrix 
$\mathbf{C}$ is the correlation matrix because $\mathbf{X'}$ is normalized.
Therefore, $\mathbf{C}$ is also directly observed as a first clue for patterns
by the most simple associations:
low absolute values indicate low correlation (and a possible independence);
high values indicate positive correlation;
negative values with a high absolute value indicate negative correlation.

\subsection{Evolution and audiovisualization of the networks}\label{sec:viz}
The evolution of the networks was observed within 
sequences of snapshots.
In each sequence,a fixed number of messages,
the window size $ws$, was used for all snapshots.
%was considered with different shifts in the message timeline to obtain snapshots.
The snapshots are disjoint in the message timeline,
and were used to perform both the PCA
with topological metrics and the Erd\"os sectioning.  
Figures and tables were usually inspected in
$ws=\{50, 100, 200, 400, 500, 800, 1000, 2000, 2500, 5000, 10000\}$ messages.
Variations in the number of vertices, edges
and other network characteristics, within the same window size $ws$,
are exposed in Section~\ref{si:frac}
of the Supporting Information document.

Network structures were mapped to video animations, sound and musical structures,
image galleries and online gadgets developed for this research~\cite{animacoes,galGMANE,appGMANE}.
Such \emph{audiovisualizations} were crucial in the initial steps and
to guide the research into the most important features of network evolution.
%Furthermore, the size of the three Erd\"os sectors could be visualized in a timeline fashion.
%Visualization of network structure was especially useful in the initial inspection of data and of the structures derived from the email lists.
